Figures for Paper

### 2021-03-09 paper_figures.Rmd
including data for the plots of the fold changes

fig1a = ggplot() +
  geom_point(data = splicing_dots_tables %>% filter(de_novo_junctions != 0),
             aes(x = deltaPSI, y =log10_test_stat,
                 alpha = graph_alpha,,fill = "Annotated Junction"), pch = 21, size = 10) + 
  geom_point(data = splicing_dots_tables %>% filter(de_novo_junctions == 0),
             aes(x = deltaPSI, y =log10_test_stat,
                 alpha = graph_alpha,fill = "Novel Junction"), pch = 21, size = 10) + 
  geom_text_repel(data = splicing_dots_tables[junction_name != ""],
                  aes(x = deltaPSI, y =log10_test_stat,
                      label = label_junction,
                      color = as.character(de_novo_junctions)), point.padding = 0.3,
                    nudge_y = 0.2,
                  min.segment.length = 0,
                  box.padding  = 2,
                  size=6,show.legend = F) +
  geom_hline(yintercept = -log10(1 - .9)) + 
  geom_vline(xintercept = -0,linetype="dotted") + 
     scale_fill_manual(name = "",
                      breaks = c("Annotated Junction", "Novel Junction"),
                      values = c("Annotated Junction" = "#648FFF", "Novel Junction" = "#fe6101") ) +
       scale_color_manual(name = "",
                      breaks = c("0", "1"),
                      values = c("1" = "#648FFF", "0" = "#fe6101") ) +
  guides(alpha = FALSE, size = FALSE) + 
  theme(legend.position = 'top') + 
  ggpubr::theme_pubr() + 
  xlab("delta PSI") + 
  ylab(expression(paste("-Lo", g[10], " Test Statistic"))) +
  theme(text = element_text(size = 24)) +
  theme(legend.text=element_text(size=22)) +
  xlim(-1,1)

@@

```{r}
rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "unc13b_nmd_exon_psi",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(name = "",
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(name = "",
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13B \nNMD Exon PSI") + 
    xlab("") + 
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28))
```

@@

rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = cryptic_psi_full, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = cryptic_psi_full),size = 12) +
    geom_smooth(aes(x = TARDBP, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A CE PSI") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') 
```

@@

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = UNC13A, y = cryptic_psi_full, fill = source),pch = 21,size = 6) + 
    stat_cor(aes(x = UNC13A, y = cryptic_psi_full),size = 12,
             method = 'spearman',
           cor.coef.name = 'rho') +
    geom_smooth(aes(x = UNC13A, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
      scale_y_continuous(labels = scales::percent) +
    ylab("UNC13A CE PSI") +
    expand_limits(y = 1) + 
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') +
      theme(text = element_text(size = 18,family = 'sans'), 
          legend.text = element_text(size = 20,family = 'sans'),
          axis.title = element_text(size = 32),
          axis.text = element_text(size = 32))
```
## UNC13A RNA and UNC13A IR
```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = UNC13A, y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = UNC13A, y = normalized_unc13a_ir),size = 12,cor.coef.name = 'rho',method = 's') +
    geom_smooth(aes(x = UNC13A, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A Normalized IR") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') 
```
## TARDBP RNA and UNC13A IR

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = normalized_unc13a_ir),size = 12) +
    geom_smooth(aes(x = TARDBP, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A Normalized IR") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') 
```

## barplot UNC13A relative RNA across experiments

@@

```{r}
stmn2 = rel_rna_cryptic_amount %>% 
  ggbarplot(,
            x = "source",
            add = c("mean_se","jitter"),
            y = "stmn_2_cryptic_psi",
            fill = 'condition',
            color = 'condition',
            position = position_dodge(0.8)) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
      values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
      values = c("#1C2617","#262114")
  ) +
  ylab("STMN2 Cryptic PSI") + 
  xlab("") + 
  guides(color = FALSE)

####barplot UNC13B normalized IR####
unc13b_ir = rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "normalized_unc13b_ir",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("Normalized UNC13B \nIntron Retention Ratio") + 
    xlab("") + 
    guides(color = FALSE) + 
      theme(legend.position = "none") +
  theme(text = element_text(size = 18)) +
      guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28))
####barplot UNC13A normalized IR####
unc13a_ir = rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "normalized_unc13a_ir",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("Normalized UNC13A \nIntron Retention Ratio") + 
    xlab("") + 
    theme(legend.position = "none") +
    guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28))

####scatterplot stmn2 normalized TARDBP####
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = stmn_2_cryptic_psi, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = stmn_2_cryptic_psi)) +
    theme(legend.position = 'bottom') 
####scatterplot UNC13BIR normalized TARDBP####
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = normalized_unc13b_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = normalized_unc13b_ir)) +
    theme(legend.position = 'bottom')
####scatterplot UNC13AIR and UNC13A Crptic####
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = cryptic_psi_full, y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = cryptic_psi_full, y = normalized_unc13a_ir)) +
    theme(legend.position = 'bottom')
####scatterplot UNC13BIR and UNC13A Crptic####
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = cryptic_psi_full, y = normalized_unc13b_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = cryptic_psi_full, y = normalized_unc13b_ir)) +
    theme(legend.position = 'bottom')+ 
  facet_wrap(~source)
```

@@

# NMD experiment on sy5y cells

@@

nmd_plot = ggbarplot(for_bar_plot_sy,
                        x = 'gene',
                        add = c("mean_se","jitter"),
                        y = 'value',
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) + 
  scale_y_continuous(labels = scales::percent) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
    values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
    values = c("#1C2617","#262114")
  )

@@

```{r onlyshort}
boxplot_table %>% 
    filter(tissue_clean %in% 
               c("Frontal Cortex", 
                 "Lumbar Spinal Cord", 
                 "Cervical Spinal Cord",
                 "Motor Cortex", 
                 "Temporal Cortex",
                 "Cerebellum") )%>% 
    group_by(disease_group2,tissue_clean) %>% 
    mutate(n_sample = n_distinct(sample)) %>% 
    ungroup() %>% 
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>% 
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex")) %>% 
    ggplot(aes(x = detection_name, 
               y = inclusion_reads * 10^6,
               fill ="red")) + 
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1)) + 
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+ 
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) + 
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) + 
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom") 
```

@@

## Side by side comparison UNC13A & STMN2 CE PSI
```{r}
clean_data_table %>% 
  # filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  # filter(unc13a_cryptic_leaf_psi > 0) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  melt() %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>%
    mutate(tissue_clean = fct_relevel(tissue_clean,"Motor Cortex", "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Temporal Cortex")) %>% 
  mutate(variable = ifelse(grepl("stmn_2",variable), "STMN2", "UNC13A")) %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(aes(color = variable)) +
  geom_jitter(aes(fill = variable),pch = 21,height = 0,width = 0.2,size = 3) +
  scale_fill_manual(values = c("#004D40","#882255")) +
  scale_color_manual(values = c("#004D40","#882255")) +
  facet_wrap(~tissue_clean,nrow = 3,scales = 'free') +
    scale_y_continuous(labels = scales::percent)  +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position = 'none')

@@

# Effect of UNC13A genotype

## UNC13A psi by genotype
```{r}
genotype_comparisons = list(c("C/C", "C/G"), c("C/C", "G/G"), c("C/G", "G/G"))

>>>>

fig1a = ggplot() +
  geom_point(data = splicing_dots_tables %>% filter(de_novo_junctions != 0),
             aes(x = deltaPSI, y =log10_test_stat,
                 alpha = graph_alpha,,fill = "Annotated Junction"), pch = 21, size = 10) + 
  geom_point(data = splicing_dots_tables %>% filter(de_novo_junctions == 0),
             aes(x = deltaPSI, y =log10_test_stat,
                 alpha = graph_alpha,fill = "Novel Junction"), pch = 21, size = 10) + 
  geom_text_repel(data = splicing_dots_tables[junction_name != ""],
                  aes(x = deltaPSI, y =log10_test_stat,
                      label = label_junction,
                      color = as.character(de_novo_junctions)), point.padding = 0.3,
                    nudge_y = 0.2,
                  min.segment.length = 0,
                  box.padding  = 2,
                  size=6,show.legend = F) +
  geom_hline(yintercept = -log10(1 - .9)) + 
  geom_vline(xintercept = -0,linetype="dotted") + 
     scale_fill_manual(name = "",
                      breaks = c("Annotated Junction", "Novel Junction"),
                      values = c("Annotated Junction" = "#648FFF", "Novel Junction" = "#fe6101") ) +
       scale_color_manual(name = "",
                      breaks = c("0", "1"),
                      values = c("1" = "#648FFF", "0" = "#fe6101") ) +
  guides(alpha = FALSE, size = FALSE) + 
  theme(legend.position = 'top') + 
  ggpubr::theme_pubr() + 
  xlab("delta PSI") + 
  ylab(expression(paste("-Lo", g[10], " Test Statistic"))) +
  theme(text = element_text(size = 24)) +
  theme(legend.text=element_text(size=22)) +
  xlim(-1,1) +
  scale_x_continuous(labels = scales::percent)

@@

```{r}
rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "condition",
              add = c("mean_se","jitter"),
              y = "unc13b_nmd_exon_psi",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8),facet.by = 'source') + 
    ggpubr::theme_pubr() +
    scale_fill_manual(name = "",
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(name = "",
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13B \nNMD Exon PSI") + 
    xlab("") + 
    guides(color = FALSE) +
    theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    facet_wrap(~source) + 
  stat_compare_means() +
  scale_y_continuous(labels = scales::percent)
```

@@

rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = cryptic_psi_full, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = cryptic_psi_full),size = 12,method = 's',cor.coef.name = 'rho') +
    geom_smooth(aes(x = TARDBP, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A CE PSI") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') +
    scale_y_continuous(labels = scales::percent)
```

@@

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = UNC13A, y = cryptic_psi_full, fill = source),pch = 21,size = 6) + 
    stat_cor(aes(x = UNC13A, y = cryptic_psi_full),size = 12,
             method = 'spearman',
           cor.coef.name = 'rho') +
    geom_smooth(aes(x = UNC13A, y = cryptic_psi_full),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
      scale_y_continuous(labels = scales::percent) +
    ylab("UNC13A CE PSI") +
    expand_limits(y = 1) + 
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') +
      theme(text = element_text(size = 18,family = 'sans'), 
          legend.text = element_text(size = 20,family = 'sans'),
          axis.title = element_text(size = 32),
          axis.text = element_text(size = 32))
```
## UNC13A RNA and UNC13A IR
```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = UNC13A, y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = UNC13A, y = normalized_unc13a_ir),size = 12,cor.coef.name = 'rho',method = 's') +
    geom_smooth(aes(x = UNC13A, y = normalized_unc13a_ir),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A Normalized IR") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') 
```
## TARDBP RNA and UNC13A IR

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = normalized_unc13a_ir),size = 12) +
    geom_smooth(aes(x = TARDBP, y = normalized_unc13a_ir),color = "black",method = 'lm') +
    ggpubr::theme_pubr() +
    theme(text = element_text(size = 20)) +
    scale_x_continuous(labels = scales::percent) +
    ylab("UNC13A Normalized IR") +
    theme(legend.title=element_blank()) +
    theme(legend.position = 'bottom') 
```

## barplot UNC13A cryptic PSI

@@

## barplot STMN2 cryptic PSI

```{r}
stmn2 = rel_rna_cryptic_amount %>% 
  ggbarplot(,
            x = "source",
            add = c("mean_se","jitter"),
            y = "stmn_2_cryptic_psi",
            fill = 'condition',
            color = 'condition',
            position = position_dodge(0.8)) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
      values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
      values = c("#1C2617","#262114")
  ) +
  ylab("STMN2 Cryptic PSI") + 
  xlab("") + 
  guides(color = FALSE)
print(stmn2)
```

## barplot UNC13B normalized IR
```{r}
unc13b_ir = rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "normalized_unc13b_ir",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("Normalized UNC13B \nIntron Retention Ratio") + 
    xlab("") + 
    guides(color = FALSE) + 
      theme(legend.position = "none") +
  theme(text = element_text(size = 18)) +
      guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28))

print(unc13b_ir)
```

## barplot UNC13A normalized IR
```{r}
unc13a_ir = rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "normalized_unc13a_ir",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("Normalized UNC13A \nIntron Retention Ratio") + 
    xlab("") + 
    theme(legend.position = "none") +
    guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28))
```

## barplot UNC13A normalized RNA Level

```{r}
text_table = fread(file.path(here::here(),"data","deseq2_cellline_fold_change.csv"))

rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "UNC13A",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13A") + 
    xlab("") + 
    theme(legend.position = "none") +
    guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.35,label = padj_plot),size = 8) + 
    geom_text(data = text_table[gene_name == "UNC13A"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)

## barplot UNC13B normalized RNA Level

```{r}
text_table = fread(file.path(here::here(),"data","deseq2_cellline_fold_change.csv"))

rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "UNC13A",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("UNC13B") + 
    xlab("") + 
    theme(legend.position = "none") +
    guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(data = text_table[gene_name == "UNC13B"],aes(x = source, y= 1.35,label = padj_plot),size = 8) + 
    geom_text(data = text_table[gene_name == "UNC13B"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)

## barplot TARDBP normalized RNA Level

```{r}
text_table = fread(file.path(here::here(),"data","deseq2_cellline_fold_change.csv"))

rel_rna_cryptic_amount %>% 
    ggbarplot(,
              x = "source",
              add = c("mean_se","jitter"),
              y = "TARDBP",
              fill = 'condition',
              color = 'condition',
              position = position_dodge(0.8)) + 
    ggpubr::theme_pubr() +
    scale_fill_manual(
        values = c("#40B0A6","#E1BE6A")
    ) + 
    scale_color_manual(
        values = c("#1C2617","#262114")
    ) +
    ylab("TARDBP") + 
    xlab("") + 
    theme(legend.position = "none") +
    guides(color = FALSE) + 
      theme(text = element_text(size = 20,family = 'sans'), 
          legend.text = element_text(size = 36,family = 'sans'),
          axis.title.y = element_text(size = 28),
          axis.text.y = element_text(size = 28)) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = source, y= 1.35,label = padj_plot),size = 8) + 
    geom_text(data = text_table[gene_name == "TARDBP"],aes(x = source, y= 1.2,label = log2FoldChange_plot),size = 8)

```
## Scatterplot stmn2 normalized TARDBP
```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = stmn_2_cryptic_psi, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = stmn_2_cryptic_psi)) +
    theme(legend.position = 'bottom')
```

## Scatterplot UNC13BIR normalized TARDBP

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = TARDBP, y = normalized_unc13b_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = TARDBP, y = normalized_unc13b_ir)) +
    theme(legend.position = 'bottom')
```

## Scatterplot UNC13A-IR and UNC13A Crptic
```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = cryptic_psi_full, 
                   y = normalized_unc13a_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = cryptic_psi_full, 
                 y = normalized_unc13a_ir)) +
    theme(legend.position = 'bottom')
```

## Scatterplot UNC13B-IR and UNC13A Crptic

```{r}
rel_rna_cryptic_amount %>% 
    filter(condition != "control") %>% 
    ggplot() + 
    geom_point(aes(x = cryptic_psi_full, y = normalized_unc13b_ir, fill = source),pch = 21,size = 4) + 
    stat_cor(aes(x = cryptic_psi_full, y = normalized_unc13b_ir)) +
    theme(legend.position = 'bottom')+ 
  facet_wrap(~source)
```

@@

# NMD experiment on SH-SY5Y cells

@@

nmd_plot = ggbarplot(for_bar_plot_sy,
                        x = 'gene',
                        add = c("mean_se","jitter"),
                        y = 'value',
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) + 
  scale_y_continuous(labels = scales::percent) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
    values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
    values = c("#1C2617","#262114")
  ) +
  ylab("Percent of transcript after CHX treatment")

@@

```{r onlyshort}
boxplot_table %>% 
    filter(tissue_clean %in% 
               c("Frontal Cortex", 
                 "Lumbar Spinal Cord", 
                 "Cervical Spinal Cord",
                 "Motor Cortex", 
                 "Temporal Cortex",
                 "Cerebellum") )%>% 
    group_by(disease_group2,tissue_clean) %>% 
    mutate(n_sample = n_distinct(sample)) %>% 
    ungroup() %>% 
    mutate(disease_group2 = gsub("Control", " Control",disease_group2)) %>% 
    mutate(detection_name = glue::glue("{disease_group2} \n ( {n_sample} )"))  %>% 
    mutate(tissue_clean = fct_relevel(tissue_clean, "Cervical Spinal Cord",
                                      "Frontal Cortex",
                                      "Lumbar Spinal Cord",
                                      "Temporal Cortex",
                                      "Motor Cortex")) %>% 
    ggplot(aes(x = detection_name, 
               y = inclusion_reads * 10^6,
               fill ="red")) + 
    geom_boxplot(show.legend = F,position = position_dodge(preserve = "single",width = 1),outlier.colour = NA)) + 
    geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+ 
    ggplot2::facet_wrap(vars(tissue_clean),scales = "free_x",nrow = 3) + 
    ylab("UNC13A cryptic \n reads per million") +
    theme(text = element_text(size = 12)) + 
    xlab("") +
    scale_fill_manual(values = colorblind_pal()(4)[2:4]) +
    theme_bw() + 
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + 
    theme(text = element_text(size = 18))  +
    theme(legend.position = "bottom") 
```

@@

## Side by side comparison UNC13A & STMN2 CE PSI
```{r}
clean_data_table %>% 
  # filter(stmn_2_cryptic_psi_leaf > 0 ) %>% 
  # filter(unc13a_cryptic_leaf_psi > 0) %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,disease_group2,tissue_clean,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  melt() %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>%
    mutate(tissue_clean = fct_relevel(tissue_clean,"Motor Cortex", "Cervical Spinal Cord",
                                    "Frontal Cortex",
                                    "Lumbar Spinal Cord",
                                    "Temporal Cortex")) %>% 
  mutate(variable = ifelse(grepl("stmn_2",variable), "STMN2", "UNC13A")) %>%
  ggplot(aes(x = variable, y = value)) +
  geom_boxplot(aes(color = variable)) +
  geom_jitter(aes(fill = variable),pch = 21,height = 0,width = 0.2,size = 3) +
  scale_fill_manual(values = c("#008574","#cd5582")) +
  scale_color_manual(values = c("#008574","#cd5582")) +
  facet_wrap(~tissue_clean,nrow = 3,scales = 'free') +
    scale_y_continuous(labels = scales::percent)  +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24))  +
  xlab("") +
  ylab("PSI")  +
  theme(legend.position = 'none')

@@

# Effect of UNC13A genotype
## UNC13A psi by genotype - rs12973192
```{r}
rs12973192_comparisons = clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  pull(detection_name) %>% 
  unique() %>% 
  combn(.,2,simplify = F)

clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12973192,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12973192) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12973192} \n ( {n_sample} )")) %>% 
  ggplot(aes(y = unc13a_cryptic_leaf_psi, x = detection_name, fill = rs12973192)) + 
  geom_boxplot() + 
  geom_jitter( height = 0) + 
  ylab("UNC13A PSI") +
  xlab("UNC13A rs12973192 Genotype") +
  scale_fill_manual(values = c("#88CCEE","#44AA99","#1B7739")) +
  ggpubr::theme_pubr() +
  theme(text = element_text(size = 24)) +
  stat_compare_means() +
  stat_compare_means(comparisons = rs12973192_comparisons,label = "p.signif") + 
  scale_y_continuous(trans='log10')
```

## UNC13A psi by genotype - rs12608932
```{r}

rs12608932_comparisons = clean_data_table %>% 
  filter(disease_tissue == T) %>% 
  filter(disease_group2 %in% c("FTLD-TDP","ALS-TDP")) %>% 
  dplyr::select(sample,tissue_clean,disease_group2,rs12608932,stmn_2_cryptic_psi_leaf,unc13a_cryptic_leaf_psi) %>% 
  mutate(tissue_clean = gsub("_"," ",tissue_clean)) %>% 
  group_by(rs12608932) %>% 
  mutate(n_sample = length(unique(sample))) %>% 
  ungroup() %>% 
  mutate(detection_name = glue::glue("{rs12608932} \n ( {n_sample} )")) %>% 
  pull(detection_name) %>% 
  unique() %>% 
  combn(.,2,simplify = F)
